\ttitle

### 2013-01-30 Chapters/Chapter2.tex
New template, merged old text

% this file is called up by thesis.tex
% content in this file will be fed into the main document

%: ----------------------- introduction file header -----------------------
\chapter{Introduction}

% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{1_introduction/figures/PNG/}{1_introduction/figures/PDF/}{1_introduction/figures/}}
\else
    \graphicspath{{1_introduction/figures/EPS/}{1_introduction/figures/}}
\fi

% ----------------------------------------------------------------------
%: ----------------------- introduction content ----------------------- 
% ----------------------------------------------------------------------

%: ----------------------- HELP: latex document organisation
% the commands below help you to subdivide and organise your thesis
%    \chapter{}       = level 1, top level
%    \section{}       = level 2
%    \subsection{}    = level 3
%    \subsubsection{} = level 4
% note that everything after the percentage sign is hidden from output

\section{Signal pre-processing and sensor fusion for timed patterns} % section 
%headings are printed smaller than chapter names
% intro

\section{Temporal segmentation}
This section will give an introduction and in-depth analysis of temporal 
segmentation. test. nog een test. test

@@

@@

%: ----------------------- HELP: special characters
% above you can see how special characters are coded; e.g. $\alpha$
% below are the most frequently used codes:
%$\alpha$  $\beta$  $\gamma$  $\delta$

%$^{chars to be superscripted}$  OR $^x$ (for a single character)
%$_{chars to be suberscripted}$  OR $_x$

%>  $>$  greater,  <  $<$  less
%≥  $\ge$  greater than or equal, ≤  $\ge$  lesser than or equal
%~  $\sim$  similar to

%$^{\circ}$C   ° as in degree C
%±  \pm     plus/minus sign

%$\AA$     produces  Å (Angstrom)

% dextran, starch, glycogen continued
%Starch of plants and glycogen of animals consists of $\alpha$-1,4-glycosidic 
%glucose polymers \cite{lastname07}. See figure \ref{largepotato} for %a 
%%comparison of glucose polymer structure and chemistry.

%Two references can be placed separated by a comma \cite{lastname07,name06}.

%: ----------------------- HELP: references
% References can be links to figures, tables, sections, or references.
% For figures, tables, and text you define the target of the link with \label{XYZ}. Then you call cross-link with the command \ref{XYZ}, as above
% Citations are bound in a very similar way with \cite{XYZ}. You store your references in a BibTex file with a programme like BibDesk.

%\figuremacro{largepotato}{A common glucose polymers}{The figure shows starch 
%granules in potato cells, taken from 
%%%\href{http://molecularexpressions.com/micro/gallery/burgersnfries/burgersnfries4.html}{Molecular
%% Expressions}.}

%: ----------------------- HELP: adding figures with macros
% This template provides a very convenient way to add figures with minimal code.
% \figuremacro{1}{2}{3}{4} calls up a series of commands formating your image.
% 1 = name of the file without extension; PNG, JPEG is ok; GIF doesn't work
% 2 = title of the figure AND the name of the label for cross-linking
% 3 = caption text for the figure

%: ----------------------- HELP: www links
% You can also see above how, www links are placed
% \href{http://www.something.net}{link text}

%\figuremacroW{lar gepotato}{Title}{Caption}{0.8}
% variation of the above macro with a width setting
% \figuremacroW{1}{2}{3}{4}
% 1-3 as above
% 4 = size relative to text width which is 1; use this to reduce figures

%: ----------------------- HELP: lists
% This is how you generate lists in LaTeX.
% If you replace {itemize} by {enumerate} you get a numbered list.

%: ----------------------- HELP: tables
% Directly coding tables in latex is tiresome. See below.
% I would recommend using a converter macro that allows you to make the table in Excel and convert them into latex code which you can then paste into your doc.
% This is the link: http://www.softpedia.com/get/Office-tools/Other-Office-Tools/Excel2Latex.shtml
% It's a Excel template file containing a macro for the conversion.

%\begin{table}[htdp]
%\centering
%\begin{tabular}{ccc} % ccc means 3 columns, all centered; alternatives are l, 
%%r
%
%{\bf Gene} & {\bf GeneID} & {\bf Length} \\ 
%% & denotes the end of a cell/column, \\ changes to next table row
%\hline % draws a line under the column headers
%
%human latexin & 1234 & 14.9 kbps \\
%mouse latexin & 2345 & 10.1 kbps \\
%rat latexin   & 3456 & 9.6 kbps \\
%% Watch out. Every line must have 3 columns = 2x &. 
%% Otherwise you will get an error.
%
%\end{tabular}
%\caption[title of table]{\textbf{title of table} - Overview of latexin genes.}
%% You only need to write the title twice if you don't want it to appear in 
%%bold in the list of tables.
%\label{latexin_genes} % label for cross-links with \ref{latexin_genes}
%\end{table}

% There you go. You already know the most important things.

% ----------------------------------------------------------------------

>>>>

% Chapter 2

\chapter{Techniques} % Main chapter title

\label{Chapter2} % For referencing the chapter elsewhere, use \ref{Chapter1}

\lhead{Chapter 2. \emph{Techniques}} % This is for the header on each 
%page - 
%perhaps a shortened title

%----------------------------------------------------------------------------------------

\section{Signal pro-processing and sensor fusion for timed patterns}

\section{Temporal Segmentation}

This section will give an introduction and in-depth analysis of temporal 
segmentation. test. nog een test. test

@@

\section{Clustering}

@@
